\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-17 paper.tex
Correct up to Fig. 8

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\usepackage{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

\maketitle
\notaL{Quité los intentos de tipografiar. Que de eso se encargue la
  revista.}
\notaL{Cambié la codificación a utf8; ya no uses latin1, es obsoleto.}
\notaL{Quité las líneas kilométricas. No te ocupes de su longitud y no
  juntes mis líneas.}
\notaL{Quité paquetes no escenciales}
\notaL{Cuida de no poner espacios al final de las líneas.}

@@

@@

\section{Theory} \label{sec:theory}
\subsection{Calculation of the current density}
\label{sec:calc-curr-dens}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the speed of attack and the width of the
porous layer. Nevertheless, it is not a simple task to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
believe a
system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be in principle be numerically calculated for a
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}}\notaL{\sout{Indica el voltaje y la
    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}
    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
  fuente de voltaje}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

This problem may be solved readily using image charge theory \cite{T1,T2}
\notaL{\sout{ref}}. The potential within the electrolytic cell coincides the
the field within an infinite vacuum containing the point charge
This problem may be solved readily using image charge theory
\notaL{ref}. The potential within the electrolytic cell coincides

@@

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique \cite{T3,T4,T5}\notaL{\sout{ref}}, which yields
 two rapidly convergingseries, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which there are no
real nor image charges, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors, and then sum over the charges that form the basis
of the 2D {\em crystal} plane and finally sum over all the
 planes \cite{T6,T7} \notaL{\sout{ref}}.
using the Ewald summation technique \notaL{ref}, which yields two rapidly converging
series, one in real space and another one in reciprocal space.
Nevertheless, as we have to evaluate the potential and the field on
the bottom of the cell to obtain the current density which attacks the
surface of the sample, and as there are no
real nor image charges there, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors, we then sum over the charges that form the basis
of the 2D {\em crystal} plane and we finally sum over all the planes \notaL{ref}.

We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{_{\bm G}}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{_{\bm G}}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{_{\bm G}}(z)-G^2\phi_{_{\bm G}}(z)=
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane given by the
symmetric solution that decays exponentially as we get away from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

\notaL{Cambié el título, pues tienes una mezcla de experimento y
  teoría aquí}
In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{Cambié las figuras}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a gold plate \notaL{Lo inventé; de qué material es
  el contacto bajo la muestra} which together make the anode. The
catode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the width, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{Controlaste/mediste la temperatura?} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
  electrodo?} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
platinum wire that with an approximate diameter of $0.5\text{mm}$.
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \notaL{referencia} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of width $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel \cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}

\subsection{Refraction Index of PS GRIN Single Layers}
\label{sec:refraction-index-ps}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  varepsilon o epsilon para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
\end{eqnarray}
\notaL{Te faltaba la igualdad}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
\label{sec:fabrication-grin-ps}
After characterizing the preparation of single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of widths $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\frac{\lambda_c}{4}$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1} which
we chose as that directly below the point-like electrode. The defect
was chosen as a half-wavelength low index layer of width $d_d$ such that
$n_Ld_L=\lambda_c/2$, and the MC has the
following sequence: $(HL)_6HH(LH )_6$. \notaL{Hay algo mal. La
  película de $\lambda/2$ fue de alto o de bajo índice? En una parte
  dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}
We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{P mayúscula
  es porosidad, o p minúscula. Checar consistencia} $P_H =0.46$, and a
width $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and width
varied, yielding a GRIN MC.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\usepackage{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

\maketitle

@@

\notaL{Si quieres ponerme algún comentario en el manuscrito usa el
  comando notaC, similar al comando notaL que uso yo}

@@

\section{Theory} \label{sec:theory}
\subsection{Calculation of the current density}
\label{sec:calc-curr-dens}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the speed of attack and the thickness of the
porous layer. Nevertheless, it is not a simple task to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
believe a
system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be in principle be numerically calculated for a
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    \notaL{El punto del electrodo hazlo más chico que el ancho
      del cable.} with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

This problem may be solved readily using image charge theory \cite{T1,T2}.
The potential within the electrolytic cell coincides

@@

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique \cite{T3,T4,T5}, which yields
two rapidly converging series, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which there are no
real nor image charges, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors, then sum over the charges that form the basis
of the 2D {\em crystal} plane, and finally sum over all the
 planes \cite{T6,T7}.

We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane given by the
symmetric solution that decays exponentially as we get away from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

\notaL{Cambié el título, pues tienes una mezcla de experimento y
  teoría aquí}
In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{Cambié las figuras}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a gold plate \notaL{Lo inventé; de qué material es
  el contacto bajo la muestra} which together make the anode. The
catode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $6.2\text{mm}\times2.03\text{cm}$) with an uncovered sample area
of about $1.21\text{cm}^2$. The height of the liquid was set at
$c=1\text{cm}$. The cathode was a
platinum wire that with a diameter of $0.41\text{mm}$ insulated by a
teflon cylinder of external diameter $2\text{mm}$. \notaL{¿Están
  bien estos diámetros?} with an uncovered tip located at $\bm r_0=(x_0,
y_0,z_0)=(0.1,0.31,0.9)$.
\notaL{Cambiar figura a una adecuada}
We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other samples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$.
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \notaL{referencia} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel \cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}

\subsection{Refraction Index of PS GRIN Single Layers}
\label{sec:refraction-index-ps}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  varepsilon o epsilon para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
\end{eqnarray}
\notaL{Te faltaba la igualdad}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
\label{sec:fabrication-grin-ps}
After characterizing the fabrication process through measurements and
calculations corresponding to single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of thickness $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\lambda_c/4$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1}) which
we chose as that directly below the point-like electrode.\notaL{Checar
  veracidad} The defect
was chosen as a half-wavelength high index layer of thickness $d_d=2d_H$ such that
$n_Hd_d=\lambda_c/2$. The MC corresponds to the
sequence $(HL)_6HH(LH )_6$ where each letter $H$ or $L$ corresponds to
a quarter wavelength plate of high and low index of refraction correspondingly.
We chose $\lambda_c= 0.67 \mu\text{m}$.\notaL{Algún motivo para esta
  elección?} For preparing the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{Explicar esta
  correspondencia entre $p$ y $n$} \notaL{P mayúscula
  es porosidad, o p minúscula. Checar consistencia} $p_H =0.46$, and a
thickness $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and thickness
varied, yielding a GRIN MC.

\section{Discussion and Results}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/G123}
  \caption{Normalized current density $j_\perp(z,0,0)/I$ calculated through
    Eq. (\ref{Eq:J}) for a
    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.03\text{cm}$ and width $b=0.62\text{cm}$, for a
    point-like electrode at $\bm r_0=(0.1\text{cm},
    0.31\text{cm},0.9\text{cm})$ (top panel). Normalized current
    along the line $y=?$ (bottom panel). \notaL{Escoger el valor de
      $y$ y poner la figura correspondiente} \notaL{Cambia los letreros, $J$ por
      $j_\perp$. La ordenada no es a, sino $x$ y la abcisa no es b
      sino $y$}.\notaL{Volverla a hacer con los datos
      correctos. Rotular la figura con la misma notación que en el
      texto. Preparar la figura como dos figuras independientes.}. }
  \label{fig:DR1}
\end{figure}
\notaL{Checar consistencia notación. $x_0$, $y_0$ y $z_0$ en
  minúsculas. Igual $j_\perp$.}
In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for the cell we built
(see Figs. \ref{f:celda} and \ref{fig:DE1}) with length
$a=2.03\text{cm}$ and width $b = 0.62\text{cm}$, the height of the
solution was taken as $c=1\text{cm}$ and we set the tip of the
electrode at $\bm
r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.31\text{cm},0.9\text{cm})$
\notaL{¿Por qué usaste estos valores?}
For these parameters we obtained $ j_\perp/I\sim
0.5-1.2\text{cm}^{-2}$.
